\LARGE \bf Planning with Attitude

### 2020-10-10 paper/main.tex
Added flexible sat stuff.

    \begin{algorithm} 
    	\begin{algorithmic}[1]
    		\caption{Multiplicative Gauss-Newton Method}\label{alg:mgn}
    		\State $k = 0$
    		\While{significant progress}
    		    \State $\bar{J} = \pdv{r(q_k)}{q} G(q_k)$ \Comment{quaternion adjusted Jacobian}
    		    \State $ \phi = -(\bar{J}^T \bar{J})^{-1} \bar{J}^T r(q_k)$ 
    		    \State $q_{k+1} = q_n \otimes \varphi{\phi}$ \Comment{apply step multiplicatively}
    		    \State $k = k + 1$
    		\EndWhile
    	\end{algorithmic}
    \end{algorithm}

    \subsection{Results}
    As illustrated in Figure \ref{fig:wahba_convergence}, it is clear that by projecting 
    back onto the unit quaternion at each iteration make initial progress, but fails to 
    exhibit the quadratic convergence typical of a Newton method. By optimizing directly 
    in the space of differential quaternions, we achieve the expected quadratic convergence.
    It should also be clear from the previous section that the adaptations to the original
    Newton method are simple and straightforward, highlighting both the effectiveness and
    value of the proposed approach.
    \begin{figure}
        \centering
        \includegraphics[width=\columnwidth, height=5cm]{figures/wahba_convergence.tikz}
        \caption{Convergence comparison for Wahba's problem. By performing Newton's method
        on the error quaternion and applying the result to the full quaternion we achieve
        quadratic convergence, whereas the more na\"ive approach doesn't converge to zero
        error. The angle error is calculated relative to the true analytical solution obtained
        via an SVD decomposition.}
        \label{fig:wahba_convergence}
    \end{figure}

@@

    \subsection{Satellite Attitude Keep-Out}
        \begin{figure}
            \centering
            \includegraphics{figures/kevins_plots/attitude_slew_plot.tikz}
            \caption{Attitude keep out}
        \end{figure}

@@

        \begin{figure}[h]
            \centering
            \includegraphics[height=4cm,width=\columnwidth]{figures/c_max_convergence.tikz}
            \caption{Constraint convergence when solving the barrell roll problem. Compares 
            the convergence of the original version of ALTRO versus the new, modified version
            that optimizing on the error state.}
            \label{fig:c_max_convergence}
        \end{figure}

>>>>

    \begin{algorithm} 
    	\begin{algorithmic}[1]
    		\caption{Multiplicative Gauss-Newton Method}\label{alg:mgn}
    		\State $k = 0$
    		\While{significant progress}
    		    \State $\bar{J} = \pdv{r(q_k)}{q} G(q_k)$ \Comment{quaternion adjusted Jacobian}
    		    \State $ \phi = -(\bar{J}^T \bar{J})^{-1} \bar{J}^T r(q_k)$ 
    		    \State $q_{k+1} = q_k \otimes \varphi(\phi)$ \Comment{apply step multiplicatively}
    		    \State $k = k + 1$
    		\EndWhile
    	\end{algorithmic}
    \end{algorithm}

    \subsection{Results}
    As illustrated in Figure \ref{fig:wahba_convergence}, it is clear that by projecting 
    back onto the unit quaternion at each iteration make initial progress, but fails to 
    exhibit the quadratic convergence typical of a Newton method. By optimizing directly 
    in the space of differential quaternions, we achieve the expected quadratic convergence.
    It should also be clear from the previous section that the adaptations to the original
    Newton method are simple and straightforward, highlighting both the effectiveness and
    value of the proposed approach.
    \begin{figure}

        \centering
        \includegraphics[width=\columnwidth, height=5cm]{figures/wahba_convergence.tikz}
        \caption{Convergence comparison for Wahba's problem. By performing Newton's method
        on the error quaternion and applying the result to the full quaternion we achieve
        quadratic convergence, whereas the more na\"ive approach doesn't converge to zero
        error. The angle error is calculated relative to the true analytical solution obtained
        via an SVD decomposition.}
        \label{fig:wahba_convergence}
    \end{figure}
    % \begin{figure}[H]
    %     \centering
    %     \includegraphics[width=\columnwidth, height=5cm]{figures/kevins_plots/convergence_plot.tikz}
    %     \caption{Convergence comparison for Wahba's problem. By performing Newton's method
    %     on the error quaternion and applying the result to the full quaternion we achieve
    %     quadratic convergence, whereas the more na\"ive approach doesn't converge to zero
    %     error.}
    %     \label{fig:wahba_convergence}
    % \end{figure}

@@

    \subsection{Satellite Attitude Keep-Out}
    A spacecraft with flexible appendages modes must perform a 150 degree slew, while making sure that a startracker does not look within 40 degrees of the sun. The flexible body spacecraft dynamics are based on the truncated hybrid coordinate model, with the three largest modes captured \cite{Tracy2020}. We can guarantee the startracker body fixed vector ($^Br_{st}$) does not look within 40 degrees of the inertial sun vector ($^Nr_{sun}$) by formulating the following constraint:
    \begin{equation}
        \langle ^N A ^B {}^Br_{st} , ^Nr_{sun}\rangle \leq \cos(40 ^\circ).
    \end{equation}
    From this constraint, an eigen-axis slew trajectory planner may violate this constraint \cite{markley2014fundamentals}. ALTRO is able to reason about the nonlinear flexible spacecraft dynamics, actuator constraints, and the startracker line of sight constraint.
        \begin{figure}
            \centering
            \includegraphics{figures/kevins_plots/attitude_slew_plot.tikz}
            \caption{Visualization of the flexible spacecraft slew with a dedicated keep out zone. Attitude is parameterized with a Rodrigues parameter to visualize in 3D. The constraint surface represents attitudes where the startracker is within 40$^\circ$ of the sun. The unconstrained solution violates this constraint, while the constrained solution is able reason about the keep out zone.}
        \end{figure}

@@

        \begin{figure}[h]
            \centering
            \includegraphics[height=4cm,width=\columnwidth]{figures/c_max_convergence.tikz}
            \caption{Constraint convergence when solving the barrel roll problem. Compares 
            the convergence of the original version of ALTRO versus the new, modified version
            that optimizing on the error state.}
            \label{fig:c_max_convergence}
        \end{figure}
